---
title: "Napoli Ballers History"
author: "Tom Gardner"
date: "August 26, 2017"
output: html_document
---

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>

<style>
  table.dataTable tbody tr.strip1 {
      background-color: #f2f2f2;
  }
  table.dataTable tbody tr.strip2 {
      background-color: #ffffff;
  }
</style>

<script type="text/javascript">
         $(document).ready(function() {
             $("#rawdata").DataTable({"pageLength":10,
                                      "stripeClasses": ['strip1', 'strip2']
                                   });
                                   
            $("#ownertable").DataTable({"pageLength":50,
                                        "bPaginate": false,
                                        "stripeClasses": ['strip1', 'strip2']
                                   });         
         } );
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html") 

library(kableExtra)
library(readxl)
library(stringr)
library(ggplot2)
library(tidyverse)
library(knitr)

# Read in raw data
data <- readxl::read_xlsx("NapoliBallersHistory.xlsx")

# Clean column names
names(data) <- str_to_lower(names(data))
names(data)[names(data) == 'pf/g'] <- "pfPerGame"
names(data)[names(data) == 'pa/g'] <- "paPerGame"
names(data)[names(data) == 'diff'] <- "pointDiff"
```

## Data

For the 8th season of the Napoli Ballers Fantasy Football League, I figured I'd go back and run some numbers on the first 7 years of the league. I scraped this data from our [historical expanded standings](http://games.espn.com/ffl/tools/finalstandings?leagueId=725705&seasonId=2016). The raw data file is [here](https://github.com/twgardner2/NapoliBallers/blob/master/NapoliBallersHistory.xlsx). This is the data itself:

```{r data, echo=FALSE}
kable(data, table.attr = "id=\"rawdata\"")
```

## Owners

TJ has done a good job of keeping Napoli Ballers alive since 2010 - especially since we are all spread across the globe, but I took a look at everyone who has been in the league:

```{r owners, echo=FALSE}
# Check owner names are unique
#table(data$owner, data$year)

kable(data %>% 
        group_by(owner) %>% 
        summarize(count = n()) %>% 
        arrange(desc(count), owner),
        table.attr = "id=\"ownertable\"") #%>% 
  #kable_styling(full_width = FALSE, position = "left") #bootstrap_options = "striped", 

```


