---
title: "Napoli Ballers History"
author: "Tom Gardner"
date: "August 26, 2017"
output: html_document
---

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>
<script src="scripts/d3.min.js"></script>

 
<style>
  table.dataTable tbody tr.strip1 {
      background-color: #f2f2f2;
  }
  table.dataTable tbody tr.strip2 {
      background-color: #ffffff;
  }
</style>

<script type="text/javascript">
         $(document).ready(function() {
             $("#rawdata").DataTable({"pageLength":10,
                                      "stripeClasses": ['strip1', 'strip2']
                                     });
            $("#ownertable").DataTable({"pageLength"     : 50,
                                        "bPaginate"      : false,
                                        "stripeClasses"  : ['strip1', 'strip2'],
                                        "order"          : [[1, "desc"]],
                                        "width"          : "25%"
                                       });
            $("#performancetable").DataTable({"pageLength"     : 50,
                                              "bPaginate"      : false,
                                              "stripeClasses"  : ['strip1', 'strip2'],
                                              "order"          : [[1, "desc"]],
                                              "width"          : "25%"
                                             });
         });
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html", self.contained=TRUE) 

library(kableExtra)
library(readxl)
library(stringr)
library(ggplot2)
library(tidyverse)
library(knitr)
library(jsonlite)

# Read in raw data
data <- readxl::read_xlsx("NapoliBallersHistory.xlsx")

# Clean columns
names(data) <- str_to_lower(names(data))
names(data)[names(data) == 'pf/g'] <- "pfPerGame"
names(data)[names(data) == 'pa/g'] <- "paPerGame"
names(data)[names(data) == 'diff'] <- "pointDiff"
data$year <- as.character(data$year)
```

## Data

For the 8th season of the Napoli Ballers Fantasy Football League, I figured I'd go back and run some numbers on the first 7 years of the league. I scraped this data from our [historical expanded standings](http://games.espn.com/ffl/tools/finalstandings?leagueId=725705&seasonId=2016). The raw data file is [here](https://github.com/twgardner2/NapoliBallers/blob/master/NapoliBallersHistory.xlsx). This is the data itself:

```{r data, echo=FALSE}
kable(data, table.attr = "id=\"rawdata\"")
```

## Owners

TJ has done a good job of keeping Napoli Ballers alive since 2010 - especially since we are all spread across the globe, but I took a look at everyone who has been in the league:

```{r owners, echo=FALSE}
# Make owner participation table
ownerTable <- data %>% 
  group_by(owner) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count), owner)

# Find unique years and owners
years <- unique(as.character(data$year))
owners <- unique(data$owner)

# Build ownerTable
for (y in years) {
  ownerTable[[y]] <- " " 
}

# Populate ownerTable
for (col in 3:ncol(ownerTable)) {
  for (row in 1:nrow(ownerTable)) {
    years_compare <- unlist(data %>% filter(owner == as.character(ownerTable[row,1])) %>% select(year))
    ownerTable[row,col] <- ifelse(  years[col-2] %in% unlist( years_compare ) ,"X"," ")
  }
}

kable(ownerTable, table.attr = "id=\"ownertable\"")
```


## Medal Table
Over the course of our league, Who has had the best results?:

``` {r performance, echo=FALSE}
# Summarize results
rankTable <- data %>% count(owner, rank)  %>% filter(rank<=3)
rankTable <- rankTable %>% spread(key = rank, value = n, fill = 0)
newNames <- c("owner", "1st Place", "2nd Place", "3rd Place")
colnames(rankTable) <- newNames

winsTable <- data %>% group_by(owner) %>% summarize(Wins = sum(w), Losses = sum(l), Ties = sum(tie))  

performanceTable <- full_join(rankTable, winsTable, by="owner") %>% mutate_all(funs(replace(., which(is.na(.)), 0)))

kable(performanceTable, table.attr = "id=\"performancetable\"")
```

<br>
If only I could quantify the amount of smack talk that goes on and compare it to this table (I'm looking at you, Jake).

<br>

That's all I've had time to look at so far, but I'd like to add pot winnings/penalties for sucking, and a few other things to this. Maybe it would be interesting to look at draft position vs. results in a given year.

<br>

Everything below this point is just stuff I'm working on and testing out:

---


``` {r medalStandJSON, echo=FALSE, results="asis"}
#jsonData <- jsonlite::toJSON( data %>% filter(rank<=3) )
#jsonData

cat(
  paste(
  '<script>
    var medalStandYears = ',toJSON(data %>% distinct(year)),';
    var medalStandData = ',toJSON(data %>% filter(rank<=3)),';
console.log(medalStandYears)    
console.log(medalStandData);
  </script>'
  , sep="")
)

```

<br>
<br>
  <select id="medalStandInput">
  </select>
<br>
<div>
  <svg id="medalTableViz" style="width:900px;height:350px;border:1px lightgray solid;" />

  
<div>

<script> <!-- Set options for select input -->

  d3.select("#medalStandInput")
    .selectAll("option")
    .data(medalStandYears)
    .enter()
    .append("option")
    .attr("value", d => {return(d.year)})
    .html(d => {return(d.year)});
    

</script>


<script> <!--Build Medal Stand -->
  var overallHeight = 300,
      standHeights = [100, 150, 75],
      standWidth = 250,
      medalStandText = ["2nd Place", "1st Place", "3rd Place"];
  
  console.log(standHeights);
  
  d3.select("#medalTableViz")
    .selectAll("g")
    .data(standHeights)
    .enter()
    .append("g")
    .attr("id", (d,i) => {return("place" + i)})
    .attr("class", "medalStand")
      .append("rect")
      .attr("x", (d,i) => {return(standWidth*i)})
      .attr("y", (d)   => {return(overallHeight-d)})
      .attr("width", standWidth)
      .attr("height", (d,i) => {return(d)})
      .attr("fill", "#f0f0f0")
      .attr("stroke", "black")
      .attr("stroke-width", "2px");

  d3.selectAll(".medalStand")
    .append("text")
    .attr("dx", (d,i) => {return(standWidth*(i+0.5))})
    .attr("dy", (d)   => {return(overallHeight-10)})
    .attr("text-anchor", "middle")
    .attr("dominant-baseline", "central")
    .attr("fill", "#4f442b")
    .text((d,i) => {return(medalStandText[i])});
        


</script>


<p style="background-color:pink; font-size:150%; color:blue"> Test inline HTML </p>


``` {r points, echo=FALSE}
# Points For plot
pfData <- data %>% filter(!is.na(pfPerGame))
pfPlot <- ggplot(pfData, aes(x=pfPerGame, fill=owner))
pfPlot + geom_histogram(aes(color=factor(ifelse(rank==1,1,0)))) + scale_color_manual(values = c("black", "red"))
```




<!-- <div id="viz"> -->
<!--   <svg style="width:1000px;height:500px;border:1px lightgray solid;"/> -->
<!-- </div> -->

<!--- d3js Code --->
<!-- <script> -->
<!--   console.log("the data is:"); -->
<!--   console.log(data); -->

<!--   d3.csv("data/circles.csv", dataViz); -->

<!--   function dataViz(data) { -->
<!--       console.log(data); -->

<!--       d3.select("svg") -->
<!--         .append("circle") -->
<!--         .attr("r", 50) -->
<!--         .attr("cx", 50) -->
<!--         .attr("cy", 50) -->
<!--         .attr("fill", "green") -->
<!--         .attr("stroke", "black") -->
<!--     } -->

<!-- </script> -->
