---
title: "Napoli Ballers History"
author: "Tom Gardner"
date: "August 26, 2017"
output: html_document
---

<link rel="stylesheet" type="text/css" href="http://cdn.datatables.net/1.10.5/css/jquery.dataTables.min.css">
<script src="http://code.jquery.com/jquery-2.1.2.min.js"></script>
<script src="http://cdn.datatables.net/1.10.5/js/jquery.dataTables.min.js"></script>
<script src="http://d3js.org/d3.v4.min.js"></script>

<style>
  table.dataTable tbody tr.strip1 {
      background-color: #f2f2f2;
  }
  table.dataTable tbody tr.strip2 {
      background-color: #ffffff;
  }
</style>

<script type="text/javascript">
         $(document).ready(function() {
             $("#rawdata").DataTable({"pageLength":10,
                                      "stripeClasses": ['strip1', 'strip2']
                                   });
                                   
            $("#ownertable").DataTable({"pageLength"     : 50,
                                        "bPaginate"      : false,
                                        "stripeClasses"  : ['strip1', 'strip2'],
                                        "order"          : [[1, "desc"]],
                                        "width"          : "25%"

                                       });
                                       
            $("#performancetable").DataTable({"pageLength"     : 50,
                                        "bPaginate"      : false,
                                        "stripeClasses"  : ['strip1', 'strip2'],
                                        "order"          : [[1, "desc"]],
                                        "width"          : "25%"

                                       });
         } );
</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html") 

library(kableExtra)
library(readxl)
library(stringr)
library(ggplot2)
library(tidyverse)
library(knitr)

# Read in raw data
data <- readxl::read_xlsx("NapoliBallersHistory.xlsx")

# Clean columns
names(data) <- str_to_lower(names(data))
names(data)[names(data) == 'pf/g'] <- "pfPerGame"
names(data)[names(data) == 'pa/g'] <- "paPerGame"
names(data)[names(data) == 'diff'] <- "pointDiff"
data$year <- as.character(data$year)
```

## Data

For the 8th season of the Napoli Ballers Fantasy Football League, I figured I'd go back and run some numbers on the first 7 years of the league. I scraped this data from our [historical expanded standings](http://games.espn.com/ffl/tools/finalstandings?leagueId=725705&seasonId=2016). The raw data file is [here](https://github.com/twgardner2/NapoliBallers/blob/master/NapoliBallersHistory.xlsx). This is the data itself:

```{r data, echo=FALSE}
kable(data, table.attr = "id=\"rawdata\"")
```

## Owners

TJ has done a good job of keeping Napoli Ballers alive since 2010 - especially since we are all spread across the globe, but I took a look at everyone who has been in the league:

```{r owners, echo=FALSE}
# Make owner participation table
ownerTable <- data %>% 
  group_by(owner) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count), owner)

# Find unique years and owners
years <- unique(as.character(data$year))
owners <- unique(data$owner)

# Build ownerTable
for (y in years) {
  ownerTable[[y]] <- " " 
}

# Populate ownerTable
for (col in 3:ncol(ownerTable)) {
  for (row in 1:nrow(ownerTable)) {
    years_compare <- unlist(data %>% filter(owner == as.character(ownerTable[row,1])) %>% select(year))
    ownerTable[row,col] <- ifelse(  years[col-2] %in% unlist( years_compare ) ,"X"," ")
  }
}


kable(ownerTable, table.attr = "id=\"ownertable\"")

```


## Medal Table
Over the course of our league, Who has had the best results?:

``` {r performance, echo=FALSE}
# Summarize results
rankTable <- data %>% count(owner, rank)  %>% filter(rank<=3)
rankTable <- rankTable %>% spread(key = rank, value = n, fill = 0)
newNames <- c("owner", "1st Place", "2nd Place", "3rd Place")
colnames(rankTable) <- newNames

winsTable <- data %>% group_by(owner) %>% summarize(Wins = sum(w), Losses = sum(l), Ties = sum(tie))  

performanceTable <- full_join(rankTable, winsTable, by="owner") %>% mutate_all(funs(replace(., which(is.na(.)), 0)))

kable(performanceTable, table.attr = "id=\"performancetable\"")

```

<br>
If only I could quantify the amount of shit-talking that goes on and compare it to this table (I'm looking at you, Jake).

<br>

That's all I had time to look at so far, but I'd like to add pot winnings/penalties for sucking, and a few other things to this. Maybe it would be interesting to look at draft position vs. results in a given year.

<p style="background-color:pink; font-size:150%; color:blue"> Test inline HTML </p>

<script>
  d3.csv("data/circles.csv", dataViz);
  
  function dataViz(data) {
    console.log(data);
  }

</script>


``` {r points, echo=FALSE}
# Points For plot
pfData <- data %>% filter(!is.na(pfPerGame))
pfPlot <- ggplot(pfData, aes(x=pfPerGame, fill=owner))
pfPlot + geom_histogram(aes(color=factor(ifelse(rank==1,1,0)))) + scale_color_manual(values = c("black", "red"))

```
