---
title: "Napoli Ballers History"
author: "Tom Gardner"
date: "August 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(sjPlot)
library(readxl)
library(stringr)
library(ggplot2)
library(tidyverse)
```

## Data

For the 8th season of the Napoli Ballers Fantasy Football League, I figured I'd go back and run some numbers on the first 7 years of the league. I scraped this data from our [historical expanded standings](http://games.espn.com/ffl/tools/finalstandings?leagueId=725705&seasonId=2016). The raw data file is [here](https://github.com/twgardner2/NapoliBallers/blob/master/NapoliBallersHistory.xlsx).

```{r data}
# Read in raw data
data <- readxl::read_xlsx("NapoliBallersHistory.xlsx")

# Clean column names
names(data) <- str_to_lower(names(data))
names(data)[names(data) == 'pf/g'] <- "pfPerGame"
names(data)[names(data) == 'pa/g'] <- "paPerGame"
names(data)[names(data) == 'diff'] <- "pointDiff"


```

## Owners

TJ has done a good job of keeping Napoli Ballers alive since 2010 - especially since we are all spread across the globe, but I took a look at everyone who has been in the league:

```{r owners}
# Check owner names are unique
table(data$owner, data$year)



```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
